\chapter{Requirement Analysis and Feasibility Study}
\section{Functional and Non-Functional Requirements}
\subsection{Functional Requirements}
\begin{enumerate}[font=\bfseries]
    \item \textbf{R1: Text Generation Model}

          \textbf{Description: }Nepali Language modeling based on both probabilistic and neural approach. Based on the trained language model, it should be able to auto generate the next word given context words.

          \begin{enumerate}
              \item \textbf{Predict next word}

                    Input: An incomplete sentence

                    Output: List of words along the probabilities of being the next word.
          \end{enumerate}
      
          \item \textbf{R2: Nepali Speech-to-Text}
          \textbf{Description: }Nepali Speech-to-Text model is to be developed and should be able to convert nepali speech to text accurately.

          \begin{enumerate}
            \item \textbf{Convert Speech To Text}
            
                  Input: Nepali Audio
                  
                  Output: Text corresponding to the input nepali audio  
          \end{enumerate}

    \item \textbf{R3: Interactive Web Application}
    
          \textbf{Description:} All the requirements should be easily accessible through a website and APIs.

          \item \textbf{R4: Browser Extension}
          
          \textbf{Description:} The text generation and speech to text should be accessible through browser extension.
\end{enumerate}

\subsection{Non-Functional Requirements}
\begin{enumerate}[font=\bfseries]
    \item \textbf{R1: Performance and scalability}
          \begin{enumerate}
              \item The load time for the user interface screens shall take no longer than 3 seconds.
              \item Queries shall return results within 3 seconds.
          \end{enumerate}
    \item \textbf{R2: Design Constraints}
          \begin{enumerate}
              \item The system shall be developed using python and postgresql databases.
          \end{enumerate}
    \item \textbf{R3: Standard Compliance}
          \begin{enumerate}
              \item The graphical user interface shall have a consistent look and feel.
          \end{enumerate}
    \item \textbf{R4: Availability}
          \begin{enumerate}
              \item The system shall be available all time.
          \end{enumerate}
    \item \textbf{R5: Portability and Compatibility}
          \begin{enumerate}
              \item The system shall be able to run in all browsers.
          \end{enumerate}
    \item \textbf{R6: Reliability and Maintainability}
          \begin{enumerate}
              \item The mean time to recover from a system failure must not be greater than 2 hours.
              \item Rate of system failure should not be greater than twice a month.
          \end{enumerate}
\end{enumerate}

\section{Hardware Requirements}
\begin{enumerate}
    \item GeForce RTX 3060 for prototype development 
    \item Minimum 32 GB RAM 
    \item Minimum 5 GB Storage for Hosting
\end{enumerate}

\section{Software Requirements}
\begin{enumerate}
    \item Programming Language : Python, Javascript
    \item Libraries : Tensorflow, keras, scikit-learn, spacy, nltk, and other python libraries 
    \item Framewoks : Django, Django Rest Framework, React
    \item Application software : Postman
    \item Target Platform : Web 
\end{enumerate}

\section{Feasibility Study}
The feasibility study encompassed different domains, including technical, economic, legal, and time-related aspects. The findings in each domain are outlined below.


\subsection{Technical Feasibility}
For our system, the required software and hardware were readily available to us. So we can state with confidence that the project is technically feasible.

\subsection{Economic Feasibility}
Since most of the hardware was already in our possession and the software used was mostly free, we can declare that the system is economically feasible.

\subsection{Legal Feasibility}
Since we are using open source data for building language model, we can state that the project is legally feasible.

\subsection{Scheduling Feasibility}
We have carefully strategized our project completion approach, employing the Agile model and breaking it down into components. It can be concluded that our timeline for project completion is viable.




